title

### 2025-03-13 docs/_tex/index.tex
reduced length. Moved content to appendices. Modified text. adjusted format. etc

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{TeX Gyre Pagella}
  \setmathfont[]{TeX Gyre Pagella Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\pagebreak

@@

There's also stark difference in public trust before the election has
occurred compared to after, a phenomenon referred to as the
``winner-loser gap''; the ``winners'' are those who supported the
winning candidate and the ``losers'' are those who supported the losing
candidate. Much research has been dedicated to analyzing the sentiment
of electoral winners vs losers, and vice versa
(\citeproc{ref-daniller2019}{Daniller and Mutz 2019};
\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Opinions of electoral
trust gathered after the election has occurred are limited considering
the well-recognized impact that the electoral outcome itself has on
feelings of public trust in elections
(\citeproc{ref-daniller2019}{Daniller and Mutz 2019}).

@@

Beyond the general competence of election workers, however, the quality
of the voter experience may be influenced merely by \emph{a priori}
impressions about \emph{who} comprises election staff and volunteers.
Political and other social science researchers have recognized for some
time the power that group identity can have over attitudes and
perception (\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
\citeproc{ref-xiao2016}{Xiao, Coppin, and Van Bavel 2016};
\citeproc{ref-xiao2012}{Xiao and Van Bavel 2012}). As such, we can
expect that information identifying the particular groups being
recruited to serve as election staff will be enough to improve trust and
confidence in election administration, and lessen expectations of
electoral fraud. The next section elaborates on why military veterans
are of particular interest in this regard.

@@

Since the results and events following the 2020 election loomed large in
anticipation of the U.S. 2024 general elections, it is reasonable to
take into account beliefs about legitimacy of the 2020 election. This
group who denies the legitimacy of the 2020 election results were
possibly the most distrusting of the 2024 election. However, given that
veteran service members are held in high regard, generally speaking,
announcing that veterans are being actively recruited to work as
election staff and volunteers is expected to positively influence
confidence in elections among those who remained firm in the belief that
the 2020 election results were illegitimate. I take into account that
legitimacy beliefs about the 2020 election and expectations of electoral
fraud are related to partisanship and include partisanship as a control
in the analysis\footnote{To be clear, I conducted an auxiliary
  regression analysis to examine the relationship between legitimacy
  beliefs and partisanship. Results revealed a statistically significant
  relationship between the two variables and thus omitting either would
  result in biased estimates.}.

@@

Finally, prior research has shown that confidence that one's own vote
would be counted as intended has been much stronger than confidence that
votes nationwide would be treated likewise
(\citeproc{ref-sances2015}{Sances and Stewart 2015};
\citeproc{ref-stewart2022}{Stewart 2022}). In other words, the public is
more trusting of elections closer to home. Taking into account that
confidence is lower for elections conducted outside of one's local area,
then information that veterans are being recruited to help conduct
elections in locations beyond one's locale may close this gap between
confidence in elections within one's local area and confidence in
elections elsewhere. Although it may be difficult to discern whether
recruiting veteran service members would improve confidence in elections
near one's local area in light of such hometown favoritism, a positive
effect on confidence in elections held beyond one's local area---where
confidence is already expectedly lower---can help discern the impact of
the group alone. Therefore, any observed disparity of confidence in
elections (i.e., the ``confidence gap'') between elections within one's
local area and elections beyond will be smaller among those who are
presented with information about election official recruitment efforts
of veteran service members.

@@

Upon construction of the two summated scales of \emph{trust} and
\emph{distrust}, internal consistency reliability coefficient \(\alpha\)
were estimated for both and found to be adequate (\(\alpha\)
\textgreater{} 0.8); the trust in elections scale \(\alpha\) = 0.93 and
the distrust scale \(\alpha\) = 0.86. In other words, the items in each
of the scales were intercorrelated well enough for each to compose a
single scale presuming a unidimensional construct for each\footnote{I
  expected item responses from the trust and distrust scales to be
  inversely correlated among the sample, but not mutually exclusive.
  Indeed, this is what I find. Polychoric correlations between the trust
  and distrust items negatively correlate as expected, as does the
  correlation between the two sum score scales. Given the ordinal nature
  of the variable items, I conducted a Spearman's rank correlation test
  (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
  correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
  Kendall's \(\tau = -0.39\)) between scores on the two scales for the
  AZ items (For the local item scale score correlation:
  \(\rho = -0.52\), \(95\%\) CI {[}-0.56, -0.48{]}; Kendall's
  \(\tau = -0.39\)). The negative correlation between the trust and
  distrust items and scores makes intuitive sense. See Appendix C for
  inter-item correlation}.

@@

The relationship is that trust and distrust represent opposing degrees
of confidence along the same spectrum. However, despite the inherent
contrast, one can hold both positive degrees of trust and distrust,
feeling similarly confident in both respects. Accordingly, equivalent
degrees of trust and distrust cancel out, rendering one relatively more
\emph{insecure} about their expectations of the future despite the fact
that they may feel confident in either direction. When trust and
distrust are considered as reflective of one's confidence about future
expectations, then both can be placed along the same spectrum. Quite
literally, this reflects an uncertain feeling of ``it could go one way
or the other'' with respect to the integrity of elections
administration. Operationally, this would reflect a middling point on a
scale of \emph{confidence}.

In light of this, I reverse coded items on the distrust scale and
combined responses to the trust in elections scale. That is, item
responses on the trust scale ranged from 0 (``Not confident at all'') to
3 (``Very confident), whereas responses on the distrust scale ranged
from 0 (''Not likely at all'') to -3 (``Very likely''). Combining
responses in this way resulted in an overall measure of \emph{confidence
in elections} to serve as the dependent variable\footnote{The
  methodological concerns between the use of (unit weighted) sum or mean
  scores compared to the use of estimated factor scores for Likert
  scales composed of multiple Likert items are legion. The use of either
  computed sum scores or estimated factor scores as a general practice
  is continuously debated (\citeproc{ref-mcneish2023}{McNeish 2023};
  \citeproc{ref-mcneish2020}{McNeish and Wolf 2020};
  \citeproc{ref-widaman2022}{Widaman and Revelle 2022},
  \citeproc{ref-widaman2024}{2024}), yet there is no general consensus
  on the most appropriate method generally. The use of either appears to
  largely depend on the researcher's particular research objective,
  theoretical suppositions, and necessity. Another common concern is the
  inappropriate treatment of ordinal variables as interval which levy
  strong assumptions, e.g., each item contributes equally to the
  variable being measured and that ordinal response categories are
  equidistant as though on an interval scale
  (\citeproc{ref-wang2013}{Wang et al. 2013}; for contrast, see
  \citeproc{ref-robitzsch2020}{Robitzsch 2020}).}. On this scale,
positive values reflect higher confidence in elections, negative values
reflect greater distrust, and values closer to zero correspond to an
individual's degree of insecurity.

The advantage is that this permits a better test of the treatment effect
as theorized. Of course, it is easy enough to examine the effect of the
treatment on both trust and distrust separately. However, the theory
presents a hypothesis that the treatment will impose influence upon both
variables \emph{concurrently and in a positive direction} with respect
to the relationship between trust and distrust. That is to say,
confidence increases insofar as trust in elections increases and
distrust decreases; since distrust detracts from trust, then an accurate
measure of confidence must take that constraint into account.

@@

\phantomsection\label{cell-fig-trustlikert}
\begin{figure}[h]

\caption{\label{fig-trustlikert}Trust in Election Administration by
Experiment Condition}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-trustlikert-1.png}}

@@

Reviewing item responses distinguished by treatment condition reveals
particulars of the treatment effect (Figure~\ref{fig-trustlikert}).
Among the items that asked about Maricopa County, AZ, it is a bit easier
to see upon which items the treatment vignette had the greatest effect.
It appears that the main effect of the treatment is upon responses to
the item that measures confidence in the security of election
technology.

@@

\phantomsection\label{cell-fig-distrustlikert}
\begin{figure}[H]

\caption{\label{fig-distrustlikert}Disrust in Election Administration by
Experiment Condition}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-distrustlikert-1.png}}

@@

Similar to the trust scale items, the items on the distrust scale were
associated with lower distrust in the treatment condition compared to
the control. A quick glance at Figure~\ref{fig-distrustlikert} shows
what appears to be a significant reduction in distrust, especially
regarding the expectations that many votes wouldn't be counted, many
voters would be turned away, and that election officials would
discourage voters from casting a ballot. Interestingly, the expectation
that there would be foreign interference in elections in Maricopa
County, AZ were pretty resilient against the treatment. And again,
responses for items pertaining to elections in one's local area are
practically indistinguishable between treatment and control.

@@

\phantomsection\label{cell-fig-dist}
\begin{figure}[H]

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-dist-1.png}}

@@

\begin{tabular}[t]{llllllllll}
\toprule
Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & df & CI\\
\midrule
Maricopa County, AZ & 0.20 & 0.93 & 0.72 & 650.00 & 637.00 & 2.96 & 0.003** & 1283.73 & {}[ 0.07, 0.33]\\
Local Area & 0.06 & 1.18 & 1.12 & 650.00 & 637.00 & 0.87 & 0.383 & 1282.95 & {}[-0.08, 0.20]\\
\bottomrule
\multicolumn{10}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{10}{l}{\rule{0pt}{1em}Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.}\\
\end{tabular}
\endgroup{}

@@

\phantomsection\label{cell-fig-legit}
\begin{figure}[!t]

\caption{\label{fig-legit}Trust in elections by treatment among those
who refute the 2020 election results}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit-1.png}}

@@

Among those who refuted the 2020 election results, trust in Maricopa
County, AZ elections was lower for each item compared to items
pertaining to elections within one's local area, regardless of treatment
condition. However, notably, trust that election technology would be
secure received the lowest confidence endorsement overall. There was
also a notable lack of trust that the voting process would be fair
relative to the other items.\footnote{What is interesting to note here
  is that the first three items regard the more human element of the
  election administration process, e.g., ensuring accuracy of counts,
  competence, and commitment of election workers. Although a neat line
  can't really be drawn between the first three and latter two items
  presented here, it is interesting to see a divergence of the usual
  high confidence placed in local area elections.} Now the comparative
difference in responses between those in the treatment group compared to
those in the control group appears substantial for items pertaining to
elections in Maricopa County, AZ.

\phantomsection\label{cell-fig-legit2}
\begin{figure}[!t]

\caption{\label{fig-legit2}Distrust in elections by treatment among
those who refute the 2020 election results}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit2-1.png}}

@@

Concerning distrust among those who refuted the 2020 election results,
responses items assessing one's expectation that election fraud would
occur reveal the same pattern. Although there is not as stark a
disparity between responses of those in the treatment and those in the
control, among those in the treatment group, there does appear to be
less expectation that election fraud would occur in Maricopa County, AZ.
Overall, review of responses to trust (Figure~\ref{fig-legit}) and
distrust survey items (Figure~\ref{fig-legit2}) does lend credence to
the impact of the treatment.

@@

\caption{\label{tbl-legit}Confidence in Elections by Treatment and
Legitimacy Beliefs}

\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-2} D{.}{.}{-2} } 
\\[-1.8ex]\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{Confidence in AZ Elections} & \multicolumn{1}{c}{w/Interaction} \\ 
\hline \\[-1.8ex] 
 Treatment & 0.18^{***}$ $(0.05) & 0.09$ $(0.06) \\ 
  Not Legitimate & -0.72^{***}$ $(0.07) & -0.86^{***}$ $(0.09) \\ 
  Republican & 0.11$ $(0.08) & 0.12$ $(0.08) \\ 
  Democrat & 0.17^{*}$ $(0.09) & 0.17^{**}$ $(0.09) \\ 
  Not Legitimate * Treatment &  & 0.27^{**}$ $(0.11) \\ 
  Constant & 0.03$ $(0.08) & 0.07$ $(0.08) \\ 
 N & \multicolumn{1}{c}{1,263} & \multicolumn{1}{c}{1,263} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.14} & \multicolumn{1}{c}{0.14} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.13} & \multicolumn{1}{c}{0.14} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.93 (df = 1258)} & \multicolumn{1}{c}{0.93 (df = 1257)} \\ 
F Statistic & \multicolumn{1}{c}{49.92$^{***}$ (df = 4; 1258)} & \multicolumn{1}{c}{41.24$^{***}$ (df = 5; 1257)} \\ 
\hline \\[-1.8ex] 
\multicolumn{3}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
\end{tabular}

The first model in Table \ref{tbl-legit} shows that overall confidence
in elections (trust - distrust) among those who read the treatment
vignette was significantly (statistically) greater than those who read
the control, on average and netting out the effects of partisanship and
legitimacy beliefs. Democratic partisanship remains marginally
significant at \(90\%\) confidence level (\(p = 0.055\)). Not believing
the 2020 election of Joe Biden was legitimate is negatively associated
with confidence in elections. In order to assess the magnitude of this
interaction effect of the treatment on those who refuted the 2020
election results, I ran a model where confidence in elections was
regressed on the interaction between the treatment and legitimacy
beliefs, controlling for partisanship.

@@

Bear in mind that confidence in elections for one's local area is
already higher than for those beyond. Thus, there's already more
insecurity concerning elections elsewhere for whatever reason. In the
anticipatory period prior to national elections, publicized efforts to
recruit veterans to work as election staff and volunteers may be a
small, but positive, step towards reducing insecurity in elections that
occur elsewhere. Especially among those who maintained a steadfast
degree of distrust in elections. Despite a lack of evidence that
systematic electoral fraud had occurred in the 2020 election, a
substantial proportion of the population were unwilling to affirm the
legitimacy of the results. However, despite such legitimacy beliefs,
most were not consistent as they expressed varying levels of trust in
different aspects of elections administration.

@@

\pagebreak

>>>>

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{TeX Gyre Pagella}
  \setmathfont[]{TeX Gyre Pagella Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\setstretch{1.25}
\pagebreak

@@

There's also stark difference in public trust before the election has
occurred compared to after, a phenomenon referred to as the
``winner-loser gap''; the ``winners'' are those who supported the
winning candidate and the ``losers'' are those who supported the losing
candidate. Much research has been dedicated to analyzing the sentiment
of electoral winners vs losers, and vice versa
(\citeproc{ref-daniller2019}{Daniller and Mutz 2019};
\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Opinions of electoral
trust gathered after the election has occurred, however, are limited
considering the well-recognized impact that the electoral outcome itself
has on feelings of public trust in elections
(\citeproc{ref-daniller2019}{Daniller and Mutz 2019}).

@@

Beyond the general competence of election workers, however, the quality
of the voter experience may be influenced merely by prior impressions
about \emph{who} comprises election staff and volunteers. Political and
other social science researchers have recognized for some time the power
that group identity can have over attitudes and perception
(\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
\citeproc{ref-xiao2016}{Xiao, Coppin, and Van Bavel 2016};
\citeproc{ref-xiao2012}{Xiao and Van Bavel 2012}). As such, we can
expect that information identifying the particular groups being
recruited to serve as election staff will be enough to improve trust and
confidence in election administration, and lessen expectations of
electoral fraud. The next section elaborates on why military veterans
are of particular interest in this regard.

@@

Since the results and events following the 2020 election loomed large in
anticipation of the U.S. 2024 general elections, it is reasonable to
take into account beliefs about legitimacy of the 2020 election. This
group who denies the legitimacy of the 2020 election results were
possibly the most apprehensive (distrusting) of the 2024 election.
However, given that veteran service members are held in high regard,
generally speaking, announcing that veterans are being actively
recruited to work as election staff and volunteers is expected to
positively influence confidence in elections among those who remained
firm in the belief that the 2020 election results were illegitimate. I
take into account that legitimacy beliefs about the 2020 election and
expectations of electoral fraud are related to partisanship and include
partisanship as a control in the analysis\footnote{To be clear, I
  conducted an auxiliary regression analysis to examine the relationship
  between legitimacy beliefs and partisanship. Results revealed a
  statistically significant relationship between the two variables and
  thus omitting either would result in biased estimates.}.

@@

Finally, prior research has shown that confidence that one's own vote
would be counted as intended has been much stronger than confidence that
votes nationwide would be treated likewise
(\citeproc{ref-sances2015}{Sances and Stewart 2015};
\citeproc{ref-stewart2022}{Stewart 2022}). In other words, the public is
more trusting of elections closer to home. Taking into account that
confidence is lower for elections conducted outside of one's local area,
then information that veterans are being recruited to help conduct
elections in locations beyond one's locale may close this gap between
confidence in elections within one's local area and confidence in
elections elsewhere. Although it may be difficult to discern whether
recruiting veteran service members would improve confidence in elections
near one's local area in light of such hometown favoritism, a positive
effect on confidence in elections held beyond one's local area---where
confidence is already expectedly lower---can help discern the impact of
the group alone on public opinion. Therefore, any observed disparity of
confidence in elections (i.e., the ``confidence gap'') between elections
within one's local area and elections beyond will be smaller among those
who are presented with information about election official recruitment
efforts of veteran service members.

@@

Upon construction of the two summated scales of \emph{trust} and
\emph{distrust}, internal consistency reliability coefficient \(\alpha\)
were estimated for both and found to be adequate (\(\alpha\)
\textgreater{} 0.8); the trust in elections scale \(\alpha\) = 0.93 and
the distrust scale \(\alpha\) = 0.86. In other words, the items in each
of the scales were intercorrelated well enough for each to compose a
single scale presuming a unidimensional construct for each\footnote{See
  Appendix C for analysis.}.

@@

In light of this, I reverse coded items on the distrust scale and
combined responses to the trust in elections scale. That is, item
responses on the trust scale ranged from 0 (``Not confident at all'') to
3 (``Very confident), whereas responses on the distrust scale ranged
from 0 (''Not likely at all'') to -3 (``Very likely''). Combining
responses in this way resulted in an overall measure of \emph{confidence
in elections} to serve as the dependent variable\footnote{The
  methodological concerns between the use of (unit weighted) sum or mean
  scores compared to the use of estimated factor scores for Likert
  scales composed of multiple Likert items are legion. The use of either
  computed sum scores or estimated factor scores as a general practice
  is continuously debated (\citeproc{ref-mcneish2023}{McNeish 2023};
  \citeproc{ref-mcneish2020}{McNeish and Wolf 2020};
  \citeproc{ref-widaman2022}{Widaman and Revelle 2022},
  \citeproc{ref-widaman2024}{2024}), yet there is no general consensus
  on the most appropriate method generally. The use of either appears to
  largely depend on the researcher's particular research objective,
  theoretical suppositions, and necessity. Another common concern is the
  inappropriate treatment of ordinal variables as interval which levy
  strong assumptions, e.g., each item contributes equally to the
  variable being measured and that ordinal response categories are
  equidistant as though on an interval scale
  (\citeproc{ref-wang2013}{Wang et al. 2013}; for contrast, see
  \citeproc{ref-robitzsch2020}{Robitzsch 2020}).}. On this scale,
positive values reflect higher confidence in elections, negative values
reflect greater distrust, and values closer to zero correspond to an
individual's degree of \emph{insecurity}.

@@

\begin{figure}[h]

\caption{\label{fig-patch10}Trust in Election Administration by
Experiment Condition}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch10-output-1.png}}

@@

Reviewing item responses distinguished by treatment condition reveals
particulars of the treatment effect (Figure~\ref{fig-patch10}). Among
the items that asked about Maricopa County, AZ, it is a bit easier to
see upon which items the treatment vignette had the greatest effect. It
appears that the main effect of the treatment is upon responses to the
item that measures confidence in the security of election technology.

@@

\caption{\label{fig-patch11}Disrust in Election Administration by
Experiment Condition}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch11-output-1.png}}

@@

Similar to the trust scale items, the items on the distrust scale were
associated with lower distrust in the treatment condition compared to
the control. A quick glance at Figure~\ref{fig-patch11} shows what
appears to be a significant reduction in distrust, especially regarding
the expectations that many votes wouldn't be counted, many voters would
be turned away, and that election officials would discourage voters from
casting a ballot. Interestingly, the expectation that there would be
foreign interference in elections in Maricopa County, AZ were pretty
resilient against the treatment. And again, responses for items
pertaining to elections in one's local area are practically
indistinguishable between treatment and control.

@@

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-dist-output-1.png}}

@@

\begin{tabular}[t]{llllllllll}
\toprule
Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & data & CI\\
\midrule
Maricopa County, AZ & 0.20 & 0.93 & 0.72 & 650.00 & 637.00 & 2.96 & 0.003** & 1283.73 & {}[ 0.07, 0.33]\\
Local Area & 0.06 & 1.18 & 1.12 & 650.00 & 637.00 & 0.87 & 0.383 & 1282.95 & {}[-0.08, 0.20]\\
\bottomrule
\multicolumn{10}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{10}{l}{\rule{0pt}{1em}Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.}\\
\end{tabular}
\endgroup{}

@@

\begin{figure}[!t]

\caption{\label{fig-patch13}Trust in elections by treatment among those
who refute the 2020 election results}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch13-output-1.png}}

@@

Among those who refuted the 2020 election results, trust in Maricopa
County, AZ elections was lower for each item compared to items
pertaining to elections within one's local area, regardless of treatment
condition. However, notably, trust that election technology would be
secure received the lowest confidence endorsement overall. There was
also a notable lack of trust that the voting process would be fair
relative to the other items.\footnote{What is interesting to note here
  is that the first three items regard the more human element of the
  election administration process, e.g., ensuring accuracy of counts,
  competence, and commitment of election workers. Although a neat line
  can't really be drawn between the first three and latter two items
  presented here, it is interesting to see a slight divergence from the
  usual high confidence placed in local area elections.} Now the
comparative difference in responses between those in the treatment group
compared to those in the control group appears substantial for items
pertaining to elections in Maricopa County, AZ.

\begin{figure}[!t]

\caption{\label{fig-patch14}Distrust in elections by treatment among
those who refute the 2020 election results}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch14-output-1.png}}

@@

Concerning distrust among those who refuted the 2020 election results,
responses items assessing one's expectation that election fraud would
occur reveal the same pattern. Although there is not as stark a
disparity between responses of those in the treatment and those in the
control, among those in the treatment group, there does appear to be
less expectation that election fraud would occur in Maricopa County, AZ.
Overall, review of responses to trust (Figure~\ref{fig-patch13}) and
distrust survey items (Figure~\ref{fig-patch14}) does lend credence to
the impact of the treatment.

@@

The first model in Table \ref{tbl-legit} shows that overall confidence
in elections among those who read the treatment vignette was
significantly (statistically) greater than those who read the control,
on average and netting out the effects of partisanship and legitimacy
beliefs. Democratic partisanship remains marginally significant at
\(90\%\) confidence level (\(p = 0.055\)). Not believing the 2020
election of Joe Biden was legitimate is negatively associated with
confidence in elections. In order to assess the magnitude of this
interaction effect of the treatment on those who refuted the 2020
election results, I ran a model where confidence in elections was
regressed on the interaction between the treatment and legitimacy
beliefs, controlling for partisanship.

@@

Bear in mind that confidence in elections for one's local area is
already higher than for those beyond. Thus, there's already more
insecurity concerning elections elsewhere for whatever reason. In the
anticipatory period prior to national elections, publicized efforts to
recruit veterans to work as election staff and volunteers may be a
small, but positive, step towards reducing insecurity in elections that
occur elsewhere. Especially among those who maintained a steadataast
degree of distrust in elections. Despite a lack of evidence that
systematic electoral fraud had occurred in the 2020 election, a
substantial proportion of the population were unwilling to affirm the
legitimacy of the results. However, despite such legitimacy beliefs,
most were not consistent as they expressed varying levels of trust in
different aspects of elections administration.

@@

\newpage

\section{Appendix A: Survey Experiment Vignettes and Survey
Items}\label{appendix-a-survey-experiment-vignettes-and-survey-items}

\subsection{Survey Experiment
Vignettes}\label{survey-experiment-vignettes}

\begin{figure}

\begin{minipage}{0.45\linewidth}

\subsubsection{Treatment Vignette}\label{treatment-vignette-1}

\textbf{Local Military Veterans Recruited for Election Jobs in Maricopa
County}\\
\strut \\
\strut ~~PHOENIX (AP) --- Election officials in Maricopa County,
Arizona, announced a program designed to recruit military veterans and
their family members from the community to serve as election
administrators, including election polling place workers, temporary
workers, and full-time staff. As the U.S. general elections in November
near, election officials must fill several thousand temporary positions
and hundreds of other open positions to ensure sufficient staffing for
the 2024 elections and beyond.\\
\strut \\
\strut ~~Army veteran Jordan Braxton just joined the elections
workforce. Jordan believes their role is important to ensuring a secure,
accurate, and transparent election, ``Many places are short on staff
this election cycle. I served my country in the Army, and I want to do
my part as a veteran and a citizen to ensure that everyone trusts the
process and the outcome of the election.''

\end{minipage}%
%
\begin{minipage}{0.10\linewidth}
~\end{minipage}%
%
\begin{minipage}{0.45\linewidth}

\subsubsection{Control Vignette}\label{control-vignette-1}

\textbf{Local Residents Recruited for Election Jobs in Maricopa
County}\\
\strut \\
\strut ~~PHOENIX (AP) ---Election officials in Maricopa County, Arizona,
announced a program to recruit members of the community to serve as
election administrators, including election polling place workers,
temporary workers, and full-time staff. As the U.S. general elections in
November near, election officials must fill several thousand temporary
positions and hundreds of other open positions to ensure sufficient
staffing for the 2024 elections and beyond.\\
\strut \\
\strut ~~Jordan Braxton just joined the elections workforce. Jordan
believes their role is important to ensuring a secure, accurate, and
transparent election, ``Many places are short on staff this election
cycle. I want to do my part as a citizen to ensure that everyone trusts
the process and the outcome of the election.''

\newpage

\subsection{Survey Items}\label{survey-items}

\caption{\label{tbl-4}Survey Items and Response Options}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{7cm}>{\raggedright\arraybackslash}p{4cm}}
\toprule
Question & response\\
\midrule
In general, how favorable or unfavorable is your impression of local election officials? & {}[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]\\
\addlinespace
Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected? & Legitimate, Not legitimate\\
\addlinespace
Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place? & Very concerned, Somewhat concerned, Not too concerned, Not at all concerned\\
\addlinespace
How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November? & Not at all confident, Not too confident, Somewhat confident, Very confident\\
\bottomrule
\end{tabu}
\endgroup{}

\newpage

\section{Appendix B: Sample Demographics and
Balance}\label{appendix-b-sample-demographics-and-balance}

\subsection{Sample Demographics}\label{sample-demographics}

The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
identified as either Non-binary/third gender (\(n = 7\)) or preferred
not to say (\(n = 9\)). A large proportion of the sample identified as
White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
held a graduate level degree (e.g., Master's, Doctorate, or Professional
level) comprised \(13\%\) of the sample; those with either degree at the
Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
had some college but no degree; and \(28.46\%\) had either a high school
level or equivalent education or less than high school. The largest
proportion of the sample identified as Democrat at \(44.64\%\), followed
by Republicans at \(42.59\%\). The proportion of true
Independents\footnote{Independent `leaners' were grouped into the
  respective party affiliation in which they lean.} was \(12.78\%\).

\caption{\label{tbl-demog}Sample Demographics}
